\begin{abstract}
As one of the most economically significant and fastest growing sectors of the
Internet, broadband networks have attracted significant interest from researchers \lois{what
are the researchers interested in doing?}. To
better understand broadband networks \lois{be more specific. Understand
what about these networks}, we developed SOAR, an open research testbed
 that utilizes computational resources provided by end users on their home wireless
routers with custom firmware. Unlike most other platforms, \sysname provides
 privacy protection of embedded device data and secures the code of donated devices
 from potentially buggy experiment codes. We find that our
platform is flexible enough to implement a variety of network measurements
including the set of devices \lois{very vague statement and this sentence has structure problems
I can not correct without talking to you.}, aggregate traffic statistics, the characteristics
    of the WiFi environment and so on despite its security restrictions.
    This paper discusses some of the challenges we faced building and using
     a platform for deploying measurement devices in home networks. We describe its design
      and implementation, demonstrate SOAR's utility with hybrid measurements,
      and characterize wireless performance from the home access point. We
       report on the makeup of home wireless networks, network traffic statistics
        and performance characteristics \lois{How do these points related to
        your main ideas? }. We believe that \sysname will provide
        valuable insights on home wireless networks and will help researchers
         to understand home networks better. \lois{This entire abstract is very vague
         and contains very little specific details}
\end{abstract}
